---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# demopkg

<!-- badges: start -->
<!-- badges: end -->

The goal of 'demopkg' is to provide some demonstrations of R functions and so vignettes. 

## Installation

You can install the development version of 'demopkg' from [GitHub](https://github.com/pabloantiqueira/demopkg) with:

``` r
devtools::install_github("https://github.com/pabloantiqueira/demopkg")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(demopkg)

M <- make_data()

```


Use this code like this...
```{r cars}
plot(rnorm(100))
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
